### 2020-05-27 intro.tex
done for today

\begin{figure*}[tb]
  \centering
  \includegraphics[width=\textwidth]{figs/chronology001.pdf}
  \caption{A seven-year tale of GPU life on a leadership class
    supercomputer: Volume of GPU swaps detected on Titan at individual
    inventories (narrow blue) and yealy sum totals for 2014 and later
    (wide gray) over its entire lifetime. High swap volumes prior to
    2014 reflect two major rework cycles on mechanical assembly issues
    at PCIe connectors that can be characterized as a break-in
    period. Our analysis in this paper excludes the break-in period
    and is focused on units in place by the end of 2013 or swapped in
    during the years that follow.}
  \label{fig:chronology}
\end{figure*}
Figure~\ref{fig:chronology} illustrates the chronology of the rework
cycles and stable periods as indicated by the number of GPU changes at
periodic inventories. The first two rework cycles before 2014
involving blade mechanical assembly can be characterized as a break-in
period on a new system that is first of its kind and pushes many
technological boundaries. The resulting field engineering as well as
data collection changes are responsible for the high GPU swap counts
before 2014. Late 2013 begins a very long period of high reliability
and stable operation with very few issues until about mid 2016, when
GPU failures begin to rise. This results in the final rework cycle,
replacing 11,000 GPUs throughout much of 2017. The peak at the end in
the figure is an artifact of turning off or ``removing'' all the
units as Titan is shut down and disassembled.

>>>>

\begin{figure*}[tb]
  \centering
  \includegraphics[width=\textwidth]{figs/chronology001.pdf}
  \caption{Volume of GPU swaps detected on Titan at individual
    inventories (narrow blue) and yealy sum totals for 2014 and later
    (wide gray) over its entire lifetime. High swap volumes prior to
    2014 reflect two major rework cycles on mechanical assembly issues
    at PCIe connectors that can be characterized as a break-in
    period. Our analysis in this paper excludes the break-in period
    and is focused on units in place by the end of 2013 or swapped in
    during the years that follow.}
  \label{fig:chronology}
\end{figure*}
Figure~\ref{fig:chronology} illustrates the chronology of the rework
cycles and stable periods as indicated by the number of GPU changes at
periodic inventories. The first two rework cycles before 2014
involving blade mechanical assembly can be characterized as a break-in
period on a new system that is first of its kind and pushes many
technological boundaries. The resulting field engineering as well as
data collection changes are responsible for the high GPU swap counts
before 2014. Late 2013 begins a very long period of high reliability
and stable operation with very few issues until about mid 2016, when
GPU failures begin to rise. This results in the final rework cycle,
replacing 11,000 GPUs throughout much of 2017. The peak at the end in
the figure is an artifact of turning off or ``removing'' all the
units as Titan is shut down and disassembled.
